\documentclass{../local}
\renewcommand{\bibname}{References}
\addcontentsline{toc}{chapter}{References}

\begin{document}

\begin{thebibliography}{9}

\bibitem{Woolridge95}
  M. Wooldridge \& N. Jennings,
  \emph{Intelligent agents: Theory and practice}.
  The Knowledge Engineering Review,
  (10(2)):115–152,
  1995.
  
  \bibitem{Zhang}
  Zhang Z. \& McCalley J. D.,
  \emph{Multiagent System Solutions for Distributed Computing, Communications, and Data Integration Needs in the Power Industry}
  
\bibitem{Koren}
Y. Koren et al,
\emph{Reconfigurable Manufacturing Systems},
CIRP Annals- Manufacturing Technology, vol. 48 no. 2, page: 527-540, 1999.

\bibitem{Puik2010}
E. Puik and L.J.M. van Moergestel,
\emph{Agile multiparallel micro manufacturing using a grid of Equiplets},
IPAS 2010 proceedings, page: 271-282, 2010.

\bibitem{FAIM2013}
D. Telgen et al,
\emph{Machine States for Distributed Control Systems for Reconfigurable Manufacturing Systems}, 2013

\bibitem{AGILEMAN}
A. Gunasekaran,
\emph{Agile manufacturing: the 21st century competitive strategy}, Elsevier, 2001. 
  
\bibitem{GRID}
Leo van Moergestel, Erik Puik and Daniel Telgen,
\emph{Production scheduling in an agile agent-based production grid}, Web Intelligence and Intelligent Agent Technology (WI-IAT), 2012 IEEE/WIC/ACM International Conferences Volume:2 Page(s):
293 - 298, 2012. 
  
\bibitem{IAT2013}
D. Telgen, L. van Moergestel, E. Puik, A. van Zanten, and A. Abdulamir,
\emph{Automatic Structured Decomposition of Manufacturing Actions in an Agent-Based Manufacturing System}
, IAT 2013

\bibitem{MASTA2013}
No Author Given, No Institute Given,
\emph{Combining Performance and Flexibility for RMS with a Hybrid Architecture}

\bibitem{PAPER70}
L. van Moergestel, No Institute Given,
\emph{Multiagent-based agile manufacturing: from user requirements to product}

\bibitem{ROS}
Morgan Quigley et al,
\emph{ROS: an open-source Robot Operating System}, Proc. Open-Source Software workshop of the International Conference on Robotics and Automation (ICRA), 2009.

\bibitem{STEWART}
Stewart, D.A,
\emph{Platform with six degrees of freedom}, Proc. Inst. Mech. Engr, Vol.180, Part I, No. 15, 1965/1966, pp. 371- 386.

\bibitem{SCRUM}
K. Schwaber, M. Beedle, \emph{Agile Software Development with Scrum.}

\end{thebibliography}
\end{document}