\documentclass{../local}
\begin{document}

%Initial situation%
In hindsight the project went pretty well. When the project initially started, we were told we had to work with three interns. At first we thought that this would have a drastic effect on our performance, but it wasnt too bad. It led to a combined effort from both sides to improve the system as much as possible. During the numerous brainstorm sessions we had in the semester, the input from the interns was invaluable.

%Teambuilding%
Throughout the semester, we semi-regularly held 'teambuilding' sessions, usually involving a certain alcoholic beverage. These session helped bring the team together, and naturally, they were loads of fun.

%state of the project when we started
When we started working on the project things were a mess. There was almost no documentation at all and we had to pretty much figure out everything for ourselves. After a couple of weeks slowly but steadily some structure was formed. Server passwords were recovered and once we got the system up and running, the real work could begin.

%Precision Fair%
In the weeks leading up to the precision fair, alot of work had to be done. Since the project was left in a pretty drastic state, we had quite some stress (and some terrible work hours as well!) getting it all together. Thanks to a lot of team effort and hard work we were able to give a proper demo, and visit the fair ourselves. During the fair the whole team(researchers \& interns) booked a hotel in Eindhoven.

%Before FAIM%
Right after the fair we had a moment to catch our breath. We used this time to write a lot of information for the wiki, to ensure that future teams will not have the same problems that we had. Around this time we also had a lot of discussions about REXOS and its structure. These discussions did not always end with a clear conclusion, but it was a lot of fun discussing it, as we all wanted to improve the system.

%FAIM%
Writing the FAIM paper put us back into 'overdrive' as with the precision fair. We had to write a simulator and gather data on a very short notice, even missing the deadline for our own thesis. Since we did learn a lot from co-writing the paper it was not too bad. 

%remainder of the project - write something nice about the research semester%
After writing the paper for FAIM our final deadlines appeared on the horizon. At the time of writing this we are pretty sleep-deprived but satisfied.

\end{document}