\documentclass{../local}

\begin{document}

\section{Abbreviations}
\begin{description}
	\item[ROS] Robot operating system
	\item[MAS] Multi-agent system
	\item[MAST] MAchine STates
	\item[GM] Grid Manufacturing
	\item[RMS] Reconfigurable manufacturing system(s)
	\item[FMS] Flexible manufacturing system(s)
	\item[HU] Hogeschool Utrecht, this is the dutch name for the University of Applied Sciences Utrecht
	\item[JADE] Java Agent DEvelopment framework
\end{description}

\section{Definition of terms}

\subsection*{Agents}
One of the most commonly known definitions, that is used throughout the project, of an agent is as defined by Wooldridge \cite{Woolridge95} \emph{"An agent is an encapsulated computer system that is situated in some environment and that is capable of flexible, autonomous action in that environment in order to meet its design objectives."}

\subsection*{REXOS}
REXOS is an abbreviated form of \emph{REQs-OS}, which is short for Reconfigurable Equiplets Operating System.

\subsection*{MAS}
A proper definition of an multi-agent system is defined by Zhang as;
\emph{"A multiagent system is a distributed system consisting of multiple software agents, 
which form “a loosely coupled network, called a multiagent 
system (MAS), to work together to solve problems that are 
beyond their individual capabilities or knowledge of each entity."}\cite{Zhang}.

\subsection*{Grid}
An collection of equiplets that is able to produce in parallel is called an grid\cite{GRID}. Where a single equiplet has limits on the complexity of the product it can create, a grid of equiplets working together can overcome these limits.

\subsection*{RMS}
According to Y. Koren RMS consist of several reconfigurable components; \emph{"A Reconfigurable Manufacturing System (RMS) is designed at the outset for rapid change in structure, as well as in hardware and software components, in order to quickly adjust production capacity and functionality within a part family in response to sudden changes in market or in regulatory requirements."}\cite{Koren}
 
\subsection*{MAST}
MAST stands for 'Machine States' of equiplets \& modules in REXOS. In order to use the equiplets properly and safely, proper machine states are needed. A previous project researched this topic, the results can be found in their paper\cite{FAIM2013}.

\subsection*{ROS}
Ros is an operating system targeted at providing core abilities to develop code for robots. According to their own site
\emph{"ROS (Robot Operating System) provides libraries and tools to help software developers create robot applications. It provides hardware abstraction, device drivers, libraries, visualizers, message-passing, package management, and more. ROS is licensed under an open source, BSD license."}\footnote{http://wiki.ros.org/}

\subsection*{Equiplet}
 In project REXOS all RMS are modular and can be reconfigured. They are named \emph{equiplets} \cite{Puik2010}. Equiplets are special production platforms that are cheap, agile and easily configurable. These platforms are able to operate in parallel.

\subsection*{Product Agent}
A product agent is a virtual representation of its product\cite{FAIM2013}. A product agent will monitor and guide the lifecycle of its product.

\subsection*{Module}
The oxford dictionary describes a module as \emph{"each of a set of standardized parts or independent units that can be used to construct a more complex structure"}\footnote{oxford dictionary}
A module within ROS is a specific piece of hardware used to perform specific actions. (eg. a pen module is used to print dots)

\subsection*{Node}
Nodes are processes that perform computational tasks. ROS is designed to be modular at a fine-grained scale: a system is typically comprised of many nodes. In this context, the term "node" is interchangable with "software module."\cite{ROS}

\subsection*{Stewart Gough platform}
The Stewart Gough Platform mechanism, originally suggested by D. Stewart in \emph{"Platform with six degrees of freedom"}\cite{STEWART}, is a parallel kinematic structure that can be used as a basis for controlled motion with 6 degrees of freedom (dof).

\subsection*{Product / service / equiplet step}
A representation of a product within the REXOS platform consists of 'product' steps. Product steps represent the various steps needed to completely construct a product. These steps are used to create service steps, a less abstract step used to calculate production time needed. Lastly service steps are used to create equiplet steps, which are instructions for the equiplet.

\end{document}
